---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ageproR

<!-- badges: start -->
<!-- badges: end -->

ageproR is a developing R-package designed to handle input data to and from 
AGEPRO (Age Structured Projection Model) calculation engine. 

> [!IMPORTANT]
>
> **If you using AGEPRO for production, please use:**
>
> - [AGEPRO-GUI, includes binary for AGEPRO calculation engine](https://github.com/nmfs-ost/AGEPRO-GUI)
> - [AGEPRO Command Line based Calculation Engine source code repo](https://github.com/noaa-pifsc/AGEPRO) 
> 

## Note

**ageproR** is still in development. These features will be implemented in future updates. 

- Predictor Recruitment Models 
- Fixed Recruitment Model 
- Empirical Cumulative Distribution Factor for w/ Linear Decline to Zero
- Markov Matrix Recruitment Model
- Run AGEPRO models with the AGEPRO calculation engine within R.
- Exported AGEPRO output R data objects.

Importing Stock Synthesis report data as AGEPRO input data is being developed as a separate R-package: ss3agepro

## Installation

You can install the development version of ageproR from 
[NOAA Fisheries OST Repository](https://github.com/nmfs-ost/ageproR) 
with:

```{r ageproR-install, eval = FALSE}
# via `pak`
install.packages("pak")
pak::pkg_install("nmfs-ost/ageproR")

# alternative method
install.packages("remotes")
remotes::install_github("nmfs-ost/ageproR")
```

## AGEPRO input file format

**ageproR** is compatible with the AGEPRO input file formats 
`AGEPRO VERSION 4.0` & `AGEPRO VERSION 4.25`. By default, **ageproR** saves 
to the `AGEPRO VERSION 4.25` Input File Format.

Please refer to the [*AGEPRO Reference Manual*](https://nmfs-ost.github.io/agepro-ref-manual/) for more technical details.

```{r example-run, child="inst/example/doc-model-workflow.Rmd"}
```

## Citation

Please cite this AGEPRO project as: 

```
Brodziak, Jon and Rago, Paul J. and Conser, Ramon. (1998). A General Approach for Making Short-Term 
Stochastic Projections from an Age-Structured Fisheries Assessment Model. Fishery Stock Assessment 
Models, 933–954. https://doi.org/10.4027/fsam.1998.52

```
The following [BibTeX](http://www.bibtex.org/) entry can be copied and used in a .bib file:

```bibtex
@article{article,
author = {Brodziak, Jon and Rago, Paul J. and Conser, Ramon},
year = {1998},
month = {01},
pages = {933-954},
title = {A General Approach for Making Short-Term Stochastic Projections from an Age-Structured Fisheries Assessment Model},
isbn = {9781566120579},
doi = {10.4027/fsam.1998.52}
}
```

<!-- Do not edit below. This adds the Disclaimer and NMFS footer. -->

****

```{r add-disclaimer, echo=FALSE, results='asis'}
url <- "https://raw.githubusercontent.com/nmfs-fish-tools/Resources/master/Disclaimer.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```

****

```{r footer, echo=FALSE, results='asis'}
url <- "https://raw.githubusercontent.com/nmfs-fish-tools/Resources/master/footer.md" 
childtext <- readLines(url)
cat(childtext, sep="\n")
```



