
## Agepro Model Workflow Examples

### Setting up a new `agepro_inp_model`
```{r set-model, eval = FALSE}
library("ageproR")

# Load path of ageproR's included Example1 Input File
inpfile <- system.file("extdata/Example1.INP", package = "ageproR")

# Load path of ageproR's included Example1 Bootstrap File
bsnfile <- system.file("extdata/Example1.BSN", package = "ageproR")

# Create a agepro_inp_model with default values
test <- ageproR::agepro_inp_model$new()
# By Default, creating a new instance of agepro_inp_model with default values will include a 
# single "NULL Recritment Model", a placeholder recruitment model. It will print a WARNING 
# to replace this Model with a vaild recruitment model before saving to file. AGEPRO  
# Calcuation Engine will not recognize NULL Recruitment models.

# Set model with Recruit Model 14: "Empirical Cumulative Distribution Function of Recruitment". 
test$set_recruit_model(c(14))

# New agepro_models instances return NULL
test$bootstrap$bootstrap_file

# Set Path of Bootstrap File 
# Note: Leaving parameter blank may request a file dialog window.
test$set_bootstrap_filename(bsnfile)
```

### Setting up a new `agepro_inp_model` w/ multiple recruitment models

```{r set-multi-recruit, eval = FALSE}
# New instance of agepro_inp_model refreses class to default values.
# Specify the "number of recuitment models" (num_rec_models) at initializtion
test <- ageproR::agepro_inp_model$new(num_rec_models=3)

# Multiple recruitments depend on agepro_model's "number of recruitment models". 
# For example, to set a 3 recruit agepro_inp_model w/ two Beverton-Holt models and a single
# Ricker model:
test$set_recruit_model(c(5,5,6)) 
# NOTE: A valid rerun of set_recruit_model will OVERWRITE the previous [RECRUIT] values.
```


### Reading or importing from AGEPRO input file (*.inp)

> [!NOTE]
> 
> Loading AGEPRO Input Files with multiple recuitment models will automatically set the
> **number of recruits** and overwrite the existing model's recruitment data; For instance,
> reading a AGEPRO input file with multiple recruits will overwrite newly created model's
> default data single NULL Recruitment.   
> 

```{r read-inp, eval = FALSE}
# New instance of agepro_inp_model refreses class to default values.
test2 <- ageproR::agepro_inp_model$new()

# Importing AGEPRO input file. 
# Leaving parameter blank may request a file dialog window.
test2$read_inp(inpfile) 

# Note: Input Files with the `AGEPRO VERSION 4.0` format can be loaded to ageproR currently, 
# but will be deprecated. In future updates. By default, AGPRO input files will be saved in the 
# `AGEPRO VERSION 4.25` format. 
# Function `read_inp` will also detect non-existant bootstrap paths. If there are no warnings, 
# check the agepro model's bootstrap filepath equals the intended "bsnpath". If not: 
# test2$set_bootstrap_filename(bsnfile)
```

### Saving to AGEPRO Input File.

```{r write-inp, eval = FALSE}
# Using the "test2" model .... 
# Using tempfile() as example filepath
outfile <- tempfile("example1_", fileext = ".inp")

# Note: Leaving parameter blank may request a file dialog window.  
test2$write_inp(outfile)
```


