
## Agepro Model Workflow Examples

### Setting up a new `agepro_inp_model`
```{r set-model, eval = FALSE}
library("ageproR")

# Load path of ageproR's included test Example1 Input File
inpfile <- file.path(find.package("ageproR"),"example/Example_UKU.INP")

# Load path of ageproR's included test Example1 Bootstrap File
bsnfile <- file.path(find.package("ageproR"),"example/Example_UKU.BSN")

# Create a agepro_inp_model with default values (This will 
test <- ageproR::agepro_inp_model$new()
# NOTE: This will give a WARNING that a NULL Recruitment Model is Found. This behavior is expected. 
# ageproR will check to see if agepro models will have NULL or invalid Recruitment models before being saved to file

# Set model with Recruit Model 14: "Empirical Cumulative Distribution Function of Recruitment". 
test$set_recruit_model(c(14))

# New agepro_models instances return NULL
test$bootstrap$bootstrap_file

# Set Path of Bootstrap File w/ 
# Note: Leaving parameter blank may request a file dialog window.
test$set_bootstrap_filename(bsnfile)

```

### Setting up a new `agepro_inp_model` w/ multiple recruitment models

```{r set-multi-recruit, eval = FALSE}
# New instance of agepro_inp_model refreses class to default values.
# Specify the number of recuitment models (num_rec_models) at initializtion
test <- ageproR::agepro_inp_model$new(num_rec_models=3)

# NOTE 2: Setting recruitment values depend on the number of recruits an agepro_model is initialized with. For example to set a `agepro_inp_model` with two Beverton-Holt and a single Ricker recruit:
test$set_recruit_model(c(5,5,6)) 
# NOTE: A valid rerun of set_recruit_model will OVERWRITE the previous [RECRUIT] values.

```


### Reading or importing from AGEPRO input file (*.inp)

> [!NOTE]
> 
> Loading AGEPRO Input Files with multiple recuitment models will automatically set the
> **number of recruits** and overwrite the existing model's recruitment data; For instance,
> reading a AGEPRO input file with multiple recruits will overwrite newly created model's
> default data single NULL Recruitment.   
> 

```{r read-inp, eval = FALSE}
# New instance of agepro_inp_model refreses class to default values.
test2 <- ageproR::agepro_inp_model$new()

# Importing AGEPRO input file. 
# Leaving parameter blank may request a file dialog window.
test2$read_inp(inpfile) 
# Note: Input Files with `AGEPRO VERSION 4.0` can be loaded to ageproR currently, but will be deprecated in future updates. By default, AGPRO input files will be saved in the AGEPRO VERSION 4.25 format. 
# Function read_inp will also detect non-existant bootstrap paths. If there are no warnings, check agepro model class bootstrap filepath equals intended "bsnpath". If not: test2$set_bootstrap_filename(bsnfile)

```

## Saving to AGEPRO Input File.

```{r write-inp, eval = FALSE}
# Using the "test2" model .... 
# Using tempfile() as example filepath
outfile <- tempfile("example1_", fileext = ".inp")
# Note: Leaving parameter blank may request a file dialog window.  
test2$write_inp(outfile)
```


